Response to the defense feedback

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

According to Definition~\ref{chapter4:def} introduced in the previous section,
the problem of quantifying the amount of leaked information can be reduced to
the problem of computing the number of items in $K^o$. However, we find that while
there are various propositional model counters (e.g., \#SAT), they are not
sufficient scalable for production cryptosystem analysis.
there is no open source modulo theories counter (\#SMT) available.

One straightforward method approximating the number of solutions is based on Monte Carlo
sampling. However, the number of satisfying values could be exponentially small.
Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
    4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
original sensitive input buffer, there is only one satisfying solution of total
$2^{32}$ possible values, which requires exponentially many samples to get a
tight bound. Monte Carlo method also suffers from the curse of dimensionality.
For example, the length of an RSA private key can be as long as 4096 bits. If we
take each byte (8 bits) in the original buffer as one symbol, the formula can
have as many as 512 symbols.

We adopt multiple-step Monte Carlo sampling methods to count the number of
possible inputs that satisfy the logic formula groups. The key idea is to split
these constraints into several small formulas and sample them independently.
We will introduce the method in the following subsection.

@@

In this section, we present the algorithm to calculate the information leakage based on Definition~\ref{chapter4:def}.

@@

However, the above sampling method fails in practice due to the following two problems:

@@

    \item The number of satisfying assignments could be exponentially small.
          According to Chernoff bound, we need exponentially many samples to
          get a tight bound.
          On an extreme situation, if the constraint only
          has one unique satisfying solution, the simple Monte Carlo method
          cannot find the satisfying assignment even after sampling many
          points.
\end{enumerate}

However, despite above two problems, we also observe two characteristics of the
problem:
\begin{enumerate}
    \item $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$ is the conjunction of
          several short constraints $c_{\addr{i}}$. The set containing the
          input variables of $c_{\addr{i}}$ is the subset of the input
          variables of $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. Some
          constraints have completely different input variables from other
          constraints.

@@

For a constraint $c_{\addr{i}}$, we define function $\pi$, which maps the
constraint into a set of different input symbols. For example, $\pi(k1 + k2 >
    128) = \{k1, k2\}$.

@@

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation in regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
\end{theorem}
With Theorem~\ref{IndependentConstraint}, we change the problem of counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.

We apply the following
algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
$c_t(\addr{1},\addr{2},\ldots,\addr{n})$.

\IncMargin{1em}
\begin{algorithm}[th]\small
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
    \For{$i\leftarrow 2$ \KwTo $n$}
    {
        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
        \For{$g_{i} \in G$}
        {
            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
            \If{$S \neq \emptyset$}
            {
                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
                \textbf{continue} \;
            }
            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
        }
    }
    \caption{The Maximum Independent Partition}
    \label{algo:max-inde}
\end{algorithm}
\DecMargin{1em}

@@

We apply the ``counting by sampling'' method. For
the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j}\\ \land ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
satisfy any constraint from $c_{i_1}$ to $c_{i_m}$. In other words, $K_{c_gi}$
should be the subset of $K_{c_1}$, $K_{c_2}$, \ldots , $K_{c_m}$. We notice that
$c_i$ usually has fewer inputs than $g_{i}$. For example, if
$c_{i_j}$ has only one 8-bit input variable, we can find the exact solution set
$K_{c_{i_j}}$ of $c_{i_j}$ by trying every possible 256 solution. After that,
we only generate random input numbers for the other input variables in
constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The detailed of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.

\IncMargin{1em}
\begin{algorithm}\small
    \SetAlgoLined
    \DontPrintSemicolon

@@

    }
    }
    \While{$n \leq \frac{8p}{1-p}$} {
        $S_{g_i}$ $\leftarrow$ $\pi(g_i)$ \;
        $v \leftarrow R(S_{g_i})$
        \If{$v$ satisfies $g_i$}
        {
            $n_s \leftarrow n_s + 1$
        }
        $n \leftarrow n +1,\ p = \frac{n_s}{n}$
    }

    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
    \caption{Multiple Step Monte Carlo Sampling}\label{chapter4:alg2}
\end{algorithm}
\DecMargin{1em}

\subsection{Error Estimation}
\label{sssec:errest}
Our result has a probabilistic guarantee that the error of the estimated amount of leaked
information is less than 1 bit under the Central Limit Theorem (CLT) and uncertainty
propagation theorem.

Let $n$ be the number of samples and $n_s$ be the number of samples that satisfy
the constraint $C$. Then we get $\hat{p} = \frac{n_s}{n}$. If we repeat the
experiment multiple times, each time we get a $\hat{p}$. As each
$\hat{p}$ is independent and identically distributed, according to the central limit
theorem, the mean value should follow the normal distribution
$ \frac{\bar{p}-E(p)}{\sigma\sqrt{n}} \rightarrow N(0,1) $. Here $E(p)$ is the
mean value of $p$, and $\sigma$ is the standard variance of $p$. If we use the
observed value $\hat{p}$ to calculate the standard deviation, we can claim that
we have 95\%\footnote{For a normal distribution, 95\% of variable $\Delta p$ fall within two sigmas of the mean.}
confidence that the error $\Delta p= \bar{p} - E(p)$ falls in the interval:
$$ |\Delta p| \leq 1.96\sqrt{\frac{ \hat{p} (1- \hat{p} )}{n}}$$

Since we use $L = \log_{2}p$ to estimate the amount of leaked information, we
can have the following error propagation formula $\Delta L = \frac{\Delta
        p}{p\ln2}$ by taking the derivative from Definition~\ref{chapter4:def}. For \tool, we want the error of estimated leaked
information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
        p}{p\ln2} \leq 1$. Therefore, as long as $ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2}$, we have
95\% confidence that the error of estimated leaked information is less than 1 bit.
During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
simulation will terminate.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.85\textwidth]{./figures/chapter4/workflow.pdf}
    \caption{The workflow of \tool{}.}
    \label{fig:workflow}
\end{figure}

@@

\subsection{Instruction Level Symbolic Execution} We model attackers'
observations from side-channel vulnerabilities with logic formulas.
Each formula captures the fine-grained information between input
secrets and leakage sites. The engine only symbolically executes
instruction that might be affected by the input sensitive data. \tool{} works on one path at a time. The memory model is conceptually similar to other offline executors (e.g., SAGE~\cite{godefroid2008automated} and the trace-based executor of BitBlaze~\cite{song2008bitblaze}). That is, we use symbolic execution to track secrets. When secrets are loaded into the memory, \tool{} starts to interpret instructions symbolically. We treat secrets as symbols ($S$). For other variables, we use concrete values ($C$) from the execution. We do not know which instruction may manipulate a secret until we execute it. For each instruction, if all its operands and implicit memory accesses are concrete values, we perform concrete calculation and update the destination with the concrete value according to the instruction semantics. Otherwise, we symbolically interpret the instruction and update the destination with a formula.

@@

@@

\begin{table}[ht]
    \centering
    %    \resizebox{.8\columnwidth}{!}{
    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
    \begin{tabular}{lr@{~}@{}l}
        \hline
        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
        Trace Logging        & 501 lines                               & of C++    \\
        Symbolic Execution   & 14,963 lines                            & of C++    \\
        Data Flow            & 451 lines                               & of C++    \\
        Monte Carlo Sampling & 603 lines                               & of C++    \\
        Others               & 211 lines                               & of Python \\ \hline
        Total                & 16,729 lines                            &           \\\hline
    \end{tabular}
    %    }
\end{table}

@@

\section{Evaluation}
\begin{table}[]
    \centering
    \small
    \caption{Evaluation results overview: Side-channel Leaks\,(Leaks),
        Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
        The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
    }\label{chapter4:table:over_result}

@@

\subsection{Overview}
In this section, we evaluate \tool{} on a series of popular crypto libraries.
In particular, we are interested in following aspects:
\begin{itemize}
\item Can \tool{} precisely report the number of leaked bits in crypto
          libraries? 
\item Are the numbers of leaked bits reported by \tool{} useful
          to justify the severity levels of the side-channel vulnerabilities?
\end{itemize}

@@

Table~\ref{chapter4:table:over_result} shows the overview of evaluation results. 
\tool{} also finds that most side-channel
vulnerabilities leak very little information in practice, which confirms our
initial assumption.  
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from severe ones.

@@

We find that the DES implementations in both mbedTLS and OpenSSL have several severe information leakages in the key schedule function. We do not see any mitigation
in the new version. We think it is not seen as worth the engineering efforts given the life cycles of DES\@.

@@

During our evaluation, we find mbed TLS 2.5 and 2.15.1 have the same
implementation of AES\@. Our tool provides the same leakage report for both
versions. \tool{} identifies that most leakages are in function
\emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by secret-dependent
memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
same. They both use a pre-computed lookup table to speed up computation.
However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)
compared to leakage 4, 5, 6, 7 (4.0 bits). We check the source code and find leakage 1, 2,
3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K
each. On the contrary, leakage 4, 5, 6, 7 each accesses a smaller lookup table
(2K). Therefore, leakage 4, 5, 6, 7 leak less information.

@@

    \subfloat[OpenSSL 1.1.0f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-0f.pdf}
        \label{fig:rsa-4}
    }
    \subfloat[OpenSSL 1.1.1]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1.pdf}
        \label{fig:rsa-5}
    }
    \subfloat[OpenSSL 1.1.1g]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1g.pdf}
        \label{fig:rsa-6}
    }
    \caption{Side-channel leakages in different implementations of RSA in OpenSSL\@. 
        We round the number of leaked information into the nearest integer. 
        The mark $*$ means timeout.}
    \label{fig:rsa}
\end{figure*}
We also evaluate \tool{} on RSA.  %, which is available online at the tool release website.
%% \jl{where?}. In general,
%% developers are interested in fixing side-channel vulnerabilities for the RSA implementations.
%% \jl{Then maybe find some space to present these results?}
 As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
versions of OpenSSL leak less information than earlier
versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
implementation for RSA\@. With this design, the sequence of squares and
multiples and the memory access patterns are independent of the secret key.
\tool{}'s result confirms the new exponentiation implementation has mitigated 
most leakages effectively because the four newer versions have fewer
leakages than version 0.9.7, which introduced this change.
OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
same amount of leakage. We check the ChangeLog and find only one change to
patch vulnerability CVE-2016-0702. 
\tool{} finds OpenSSL 1.1.1 and 1.1.1g have significantly less
leaked information than other versions.
We check the ChangeLog of these two versions and find a claim that
the new RSA implementation adopts ``numerous side-channel attack mitigation'', 
which proves the effectiveness of our quantifying method.
%We also observe the latest version (1.1.1g) contains some new leakages. We have
%contacted the developers and they have confirmed our findings.

Our quantification result shows vulnerabilities
that leak significant amounts of information
are more likely to be fixed in the updated version.
As presented in Figure~\ref{fig:rsa}, 
OpenSSL 0.9.7 has several severe leaks from
function \textsf{bn\_sqr\_comba8}, which is a main 
component of the OpenSSL big number implementation.
Shown in Figure~\ref{fig:old_sqr2}, it has a 
secret-dependent control flow at line 8.
The value of the function parameter \textbf{a} is derived from
the secret key. 
As function \textsf{bn\_sqr\_comba8}
calls the macro (\textsf{sqr\_add\_c2}) multiple times, 
and the code can leak some information each time.
\tool{} indicates the vulnerability is quite serious. 
It was patched in OpenSSL 1.1.1\@. In 
Figure~\ref{fig:new_sqr2}, control-flows transfers are replaced
so there are no leaks in the function
\textsf{sqr\_add\_c2} in OpenSSL 1.1.1\@. We note
that line 4 and 9 in Figure~\ref{fig:old_sqr2} both contain if branches.
However, they are not leaks because
most compilers use \emph{add with carry} instruction to eliminate the branch.
In addition, branches can be compiled into non-branch machine instructions 
with conditional moves. 
We notice a bitwise operation in Libgcrypt 1.8.5 is compiled to a conditional 
jump, which leads to a side-channel leakage.
Therefore, source-level code reviews are not accurate
enough to detect side-channels.

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

>>>>

According to Definition~\ref{chapter4:def} introduced in the previous section,
the problem of quantifying the amount of leaked information can be reduced to
the problem of computing the number of items in $K^o$. However, we find that while
there are various propositional model counters (e.g., \#SAT), they are not
sufficiently scalable for production cryptosystem analysis.
Besides, there is no open source modulo theories counter (\#SMT) available.

One straightforward method to approximate the number of solutions is based on Monte Carlo
sampling. However, the number of satisfying values could be exponentially small.
Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
    4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
original sensitive input buffer, there is only one satisfying solution of total
$2^{32}$ possible values, which requires exponentially many samples to get a
tight bound. Monte Carlo method also suffers from the curse of dimensionality.
For example, the length of an RSA private key can be as long as 4096 bits. If we
take each byte (8 bits) in the original buffer as one symbol, the formula can
have as many as 512 symbols.

We adopt multiple-step Monte Carlo sampling methods to count the number of
possible inputs that satisfy the logic formula groups. The key idea is to split
these constraints into several small formulas and sample them independently.
We will introduce the method in the following subsection. In this section, we present the algorithm to calculate the information leakage based on Definition~\ref{chapter4:def}.

@@

@@

However, the above sampling method fails in practice due to the following two problems.

@@

    \item The number of satisfying assignments could be exponentially small.
          According to the Chernoff bound~\cite{hoeffding1994probability}, we need exponentially many samples to
          get a tight bound.
          On an extreme situation, if the constraint only
          has one unique satisfying solution, the simple Monte Carlo method
          cannot find the satisfying assignment even after sampling many
          points.
\end{enumerate}

However, despite the above two problems, we also observe two characteristics of the
problem:
\begin{enumerate}
    \item $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$ is the conjunction of
          several short constraints $c_{\addr{i}}$. The set containing the
          input variables of $c_{\addr{i}}$ is the subset of the input
          variables of $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. Some
          constraints have completely different input variables from other
          constraints.

@@

For a constraint $c_{\addr{i}}$, we define function $\pi$, which projects the
constraint into a set of different input symbols. For example, $\pi(k1 + k2 >
    128) = \{k1, k2\}$.

@@

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation with regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
\end{theorem}
With Theorem~\ref{IndependentConstraint}, we change the problem of counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.

We apply 
Algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
$c_t(\addr{1},\addr{2},\ldots,\addr{n})$.

\IncMargin{1em}
\begin{algorithm}[th]\normalsize
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
    \For{$i\leftarrow 2$ \KwTo $n$}
    {
        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
        \For{$g_{i} \in G$}
        {
            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
            \If{$S \neq \emptyset$}
            {
                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
                \textbf{continue} \;
            }
            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
        }
    }
    \caption{The Maximum Independent Partition}
    \label{algo:max-inde}
\end{algorithm}
\DecMargin{1em}

@@

We apply the ``counting by sampling'' method. For
the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j}\\ \land ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
satisfy any constraint from $c_{i_1}$ to $c_{i_m}$. In other words, $K_{c_gi}$
should be the subset of $K_{c_1}$, $K_{c_2}$, \ldots , $K_{c_m}$. We notice that
$c_i$ usually has fewer inputs than $g_{i}$. For example, if
$c_{i_j}$ has only one 8-bit input variable, we can find the exact solution set
$K_{c_{i_j}}$ of $c_{i_j}$ by trying every possible 256 solution. After that,
we only generate random input numbers for the other input variables in
constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The details of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.

\IncMargin{1em}
\begin{algorithm}\normalsize
    \SetAlgoLined
    \DontPrintSemicolon

@@

    }
    }
    \While{$n \leq \frac{8p}{1-p}$} {
        $S_{g_i}$ $\leftarrow$ $\pi(g_i)$ \;
        $v \leftarrow R(S_{g_i})$ \;
        \If{$v$ satisfies $g_i$}
        {
            $n_s \leftarrow n_s + 1$
        }
        $n \leftarrow n +1,\ p = \frac{n_s}{n}$
    }

    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * \mathrm{range(k)})$
    \caption{Multiple Step Monte Carlo Sampling}\label{chapter4:alg2}
\end{algorithm}
\DecMargin{1em}

\subsection{Error Estimation}
\label{sssec:errest}
Our result has a probabilistic guarantee that the error of the estimated amount of leaked
information is less than 1 bit under the Central Limit Theorem (CLT) and uncertainty
propagation theorem~\cite{walpole1993probability}.

Let $n$ be the number of samples and $n_s$ be the number of samples that satisfy
the constraint $C$. Then we get $\hat{p} = \frac{n_s}{n}$. If we repeat the
experiment multiple times, each time we get a $\hat{p}$. As each
$\hat{p}$ is independent and identically distributed, according to the central limit
theorem, the mean value should follow the normal distribution
$$ \frac{\bar{p}-E(p)}{\sigma\sqrt{n}} \rightarrow N(0,1). $$ Here $E(p)$ is the
mean value of $p$, and $\sigma$ is the standard variance of $p$. If we use the
observed value $\hat{p}$ to calculate the standard deviation, we can claim that
we have 95\%\footnote{For a normal distribution, 95\% of variable $\Delta p$ fall within two sigmas of the mean.}
confidence that the error $\Delta p= \bar{p} - E(p)$ falls in the interval:
$$ |\Delta p| \leq 1.96\sqrt{\frac{ \hat{p} (1- \hat{p} )}{n}}.$$

Since we use $L = \log_{2}p$ to estimate the amount of leaked information, we
can have the following error propagation formula $\Delta L = \frac{\Delta
        p}{p\ln2}$ by taking the derivative from Definition~\ref{chapter4:def}. For \tool, we want the error of estimated leaked
information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
        p}{p\ln2} \leq 1$. Therefore, as long as $$ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2},$$ 
\noindent we have 95\% confidence that the error of estimated leaked information is less than 1 bit.
During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
simulation will terminate.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.95\textwidth]{./figures/chapter4/workflow.pdf}
    \caption{The workflow of \tool{}.}
    \label{fig:workflow}
\end{figure}

@@

\subsection{Instruction Level Symbolic Execution} We model an attacker's
observations from side-channel vulnerabilities with logic formulas.
Each formula captures the fine-grained information between the input
secrets and leakage sites. The engine only symbolically executes
instruction that might be affected by the input sensitive data. \tool{} works on one path at a time. The memory model is conceptually similar to other offline executors (e.g., SAGE~\cite{godefroid2008automated} and the trace-based executor of BitBlaze~\cite{song2008bitblaze}). That is, we use symbolic execution to track secrets. When secrets are loaded into the memory, \tool{} starts to interpret instructions symbolically. We treat secrets as symbols ($S$). For other variables, we use concrete values ($C$) from the execution. We do not know which instruction may manipulate a secret until we execute it. For each instruction, if all its operands and implicit memory accesses are concrete values, we perform concrete calculation and update the destination with the concrete value according to the instruction semantics. Otherwise, we symbolically interpret the instruction and update the destination with a formula.

@@

\subsection{Implementation}

@@

\begin{table}[ht]
    \centering\normalsize
    %    \resizebox{.8\columnwidth}{!}{
    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
    \begin{tabular}{lr@{~}@{}l}
        \hline
        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
        Trace Logging        & 501 lines                               & of C++    \\
        Symbolic Execution   & 14,963 lines                            & of C++    \\
        Data Flow            & 451 lines                               & of C++    \\
        Monte Carlo Sampling & 603 lines                               & of C++    \\
        Others               & 211 lines                               & of Python \\ \hline
        Total                & 16,729 lines                            &           \\\hline
    \end{tabular}
    %    }
\end{table}

@@

\section{Evaluation}
\begin{table}[]
    \centering
    \small
    \caption{Evaluation results overview: Side-channel Leaks\,(Leaks),
        Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
        the number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
    }\label{chapter4:table:over_result}

@@

\subsection{Overview}
In this section, we evaluate \tool{} on a set of popular crypto libraries.
In particular, we are interested in following aspects:
\begin{itemize}
\item Can \tool{} precisely report the number of leaked bits in crypto
          libraries? 
\item Are the numbers of leaked bits reported by \tool{} useful
          to justify the severity levels of the side-channel vulnerabilities?
\end{itemize}

@@

Table~\ref{chapter4:table:over_result} shows an overview of the evaluation results. 
\tool{} also finds that most side-channel
vulnerabilities leak very little information, which confirms our
initial assumption.  
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from the severe ones.

@@

We find that the DES implementations in both mbedTLS and OpenSSL have several severe information leakages in the key-schedule function. We do not see any mitigation
in the new version. We think it is not seen as worth the engineering efforts given the life cycles of DES\@.

@@

During our evaluation, we find mbed TLS 2.5 and 2.15.1 have the same
implementation of AES\@. Our tool provides the same leakage report for both
versions. \tool{} identifies that most leakages are in function
\emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by the secret-dependent
memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
same. They both use a pre-computed lookup table to speed up computation.
However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)
compared to leakage 4, 5, 6, 7 (4.0 bits). We check the source code and find leakage 1, 2,
3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K
each. On the contrary, leakage 4, 5, 6, 7 each accesses a smaller lookup table
(2K). Therefore, leakage 4, 5, 6, 7 leak less information.

@@

    \subfloat[OpenSSL 1.1.0f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-0f.pdf}
        \label{fig:rsa-4}
    }
    \subfloat[OpenSSL 1.1.1]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1.pdf}
        \label{fig:rsa-5}
    }
    \subfloat[OpenSSL 1.1.1g]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1g.pdf}
        \label{fig:rsa-6}
    }
    \caption{Side-channel leakages in different implementations of RSA in OpenSSL\@. 
        We round the number of leaked information into the nearest integer. 
        The mark $*$ means timeout.}
    \label{fig:rsa}
\end{figure*}
We also evaluate \tool{} on RSA.  %, which is available online at the tool release website.
%% \jl{where?}. In general,
%% developers are interested in fixing side-channel vulnerabilities for the RSA implementations.
%% \jl{Then maybe find some space to present these results?}
 As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
versions of OpenSSL leak less information than the earlier
versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
implementation for RSA\@. With this design, the sequence of squares and
multiples and the memory access patterns are independent of the secret key.
\tool{}'s result confirms the new exponentiation implementation has mitigated 
most leakages effectively because the four newer versions have fewer
leakages than version 0.9.7, which introduced this change.
OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
same amount of leakage. We check the ChangeLog and find only one change to
patch vulnerability CVE-2016-0702. 
\tool{} finds OpenSSL 1.1.1 and 1.1.1g have significantly less
leaked information than other versions.
We check the ChangeLog of these two versions and find a claim that
the new RSA implementation adopts ``numerous side-channel attack mitigation'', 
which proves the effectiveness of our quantifying method.
%We also observe the latest version (1.1.1g) contains some new leakages. We have
%contacted the developers and they have confirmed our findings.

Our quantification result shows vulnerabilities
that leak significant amounts of information
are more likely to be fixed in the updated version.
As presented in Figure~\ref{fig:rsa}, 
OpenSSL 0.9.7 has several severe leaks from
function \textsf{bn\_sqr\_comba8}, which is a main 
component of the OpenSSL big number implementation.
Shown in Figure~\ref{fig:old_sqr2}, it has a 
secret-dependent control flow at line 8.
The value of the function parameter \texttt{a} is derived from
the secret key. 
As function \textsf{bn\_sqr\_comba8}
calls the macro (\textsf{sqr\_add\_c2}) multiple times, 
and the code can leak some information each time.
\tool{} indicates the vulnerability is quite severe. 
It was patched in OpenSSL 1.1.1\@. In 
Figure~\ref{fig:new_sqr2}, control-flows transfers are replaced
so there are no leaks in the function
\textsf{sqr\_add\_c2} in OpenSSL 1.1.1\@. We note
that line 4 and 9 in Figure~\ref{fig:old_sqr2} both contain \texttt{if} branches.
However, they are not leaks because
most compilers use \emph{add with carry} instruction to eliminate the branch.
In addition, branches can be compiled into non-branch machine instructions 
with conditional moves. 
We notice a bitwise operation in Libgcrypt 1.8.5 is compiled to a conditional 
jump, which leads to a side-channel leakage.
Therefore, source-level code reviews are not accurate
enough to detect side-channels.

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \texttt{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();
